Parenting observation lexical diversity - Exp 1

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
exp1 lexical diversity results integrated

author-information: > 
    \author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
    \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
    \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}

@@

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

@@

```{r, echo=F}
e1path = "../../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep=''))

@@

@@

For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

@@

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

@@

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

>>>>

author-information: > 
    \author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
    {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\
    {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\ 
    Department of Psychology, Stanford University \\ 
    Palo Alto, CA 94301 USA}

@@

output: cogsci2016::cogsci_paper
final-submission: \cogscifinalcopy
---

@@

```{r libraries, echo=F, include=F}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
source("multiplot.R")

select <- dplyr::select # masked by MASS
theme_set(theme_few())
```

@@

```{r, echo=F}
e1path = "../../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting

@@

```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))

ms_lex <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col="TTR") # Type/Token Ratio

ttr_means <- d%>%
  group_by(Condition)%>%
  summarise(mean = mean(TTR), sd = sd(TTR))

# report table with ttr_means lex_sds

e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_lex_mtld <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col="MTLD")

mtld_means <- d %>%
  group_by(Condition)%>%
  summarise(mean = mean(MTLD), sd=sd(MTLD))

# report table with mtld_means _sds

e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("MTLD") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
  theme(legend.position="none")

multiplot(e1ttr, e1mtld, cols=2)
```

Word tokens and word types

```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
ms_tok <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "tokens")

e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) +geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

ms_type <- d %>% group_by(Condition) %>%
  multi_boot_standard(col = "types")

e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized() + ggthemes::theme_few() +
  theme(legend.position="none")

multiplot(e1tokens, e1types, cols=2)
```

@@

@@

@@

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
exp1 lexical diversity results integrated

% KM added 1/4/18 to allow control of blind submission

@@

\author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}

@@

@@

For more information on citations in RMarkdown, see
\textbf{\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html\#citations}{here}.}

@@

You can read local images using png package for example and plot it like
a regular plot using grid.raster from the grid package. With this method
you have full control of the size of your image. \textbf{Note: Image
must be in .png file format for the readPNG function to work.}

@@

\subsection{One-column images}\label{one-column-images}

Single column is the default option, but if you want set it explicitly,
set \texttt{fig.env} to \texttt{figure}. Notice that the
\texttt{num.cols} option for the caption width is set to \texttt{1}.

>>>>

% KM added 1/4/18 to allow control of blind submission
\cogscifinalcopy

@@

\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Palo Alto, CA 94301 USA}

@@

{\centering \includegraphics{figs/e1lex_div-1}

\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.}\label{fig:e1lex_div}
\end{figure}
\end{CodeChunk}

Word tokens and word types

{\centering \includegraphics{figs/e1token_type-1}

\caption[Mean number of word types and word tokens by condition in Experiment 1]{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
\end{figure}
\end{CodeChunk}

@@

@@

@@

### 2019-02-08 parenting_obs_e1/parenting_obs_lexdiv.Rmd
exp1 lexical diversity results integrated

```{r}
#data <- read.csv("lexdiv_data.csv", header=TRUE) # Emily's TTR calculation
data <- read.csv("MTLD_HDD.csv", header=TRUE) # Vivian's new TTR, MTLD, and HDD pipeline (generated by get_all_parent_speech.py)
data$SID = data$sid
data$sid = NULL
data$X = NULL
#dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
#dem_anon = dem[,c("SID","age","gender","ethnicity","english","parent_ed","num_lang","Exclude")]
#write.csv(dem_anon, file="anonymized_demographics_parenting_obs_e1.csv")
dem <- read.csv("anonymized_demographics_parenting_obs_e1.csv", header=T)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData") # do we use this??

@@

```{r}
d <- left_join(data, conditions)%>%
  left_join(dem)%>%
  transmute(sid=SID, 
            types = types,
            tokens = tokens, 
            TTR = TTR, 
            MTLD = MTLD,
            condition = Condition, 
            video = Video, 
            age = age,
            gender = gender,
            parent_ed = parent_ed)%>%
  left_join(ids)%>%
  filter(!is.na(condition))
```

@@

ggplot(ms_tok, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()
ggsave(file="figs/e1_word_types.pdf", width=3, height=3)
```

@@

Prepare data.
```{r}
lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         lexdiv = as.numeric(lexdiv),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))
```

##Lexical diversity
Predicting lexical diversity based on experimental condition, PAQ, demographics. 
```{r}
maximal_mod <- lmer(lexdiv ~ condition  + age + gender + parent_ed +
                           (1| video), 
                         data = lmer_data)
summary(maximal_mod)

@@

M1 <- lex_means$mean[1]
M2 <- lex_means$mean[2]
SD1 <- lex_sds$sd[1]
SD2 <- lex_sds$sd[2]

>>>>

```{r}
#data <- read.csv("lexdiv_data.csv", header=TRUE) # Emily's TTR calculation
data <- read.csv("MTLD_HDD.csv", header=TRUE) # Vivian's new TTR, MTLD, and HDD pipeline (generated by get_all_parent_speech.py)
data$SID = data$sid
data$sid = NULL
data$X = NULL
#dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
#dem_anon = dem[,c("SID","age","gender","ethnicity","english","parent_ed","num_lang","Exclude")]
#write.csv(dem_anon, file="anonymized_demographics_parenting_obs_e1.csv")
dem <- read.csv("anonymized_demographics_parenting_obs_e1.csv", header=T)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData") # do we use this?? GK: yes, see left_join on line 76

@@

```{r}
d <- left_join(data, conditions)%>%
  left_join(dem)%>%
  transmute(sid=SID, 
            types = types,
            tokens = tokens, 
            TTR = TTR, 
            MTLD = MTLD,
            condition = Condition, 
            video = Video, 
            age = age,
            gender = gender,
            parent_ed = parent_ed)%>%
  left_join(ids)%>%
  filter(!is.na(condition))

save(d, file="Exp1_cleaned_data.RData") # for use in paper.Rmd
```

@@

ggplot(ms_type, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()
ggsave(file="figs/e1_word_types.pdf", width=3, height=3)
```

@@

Prepare data.
```{r}
lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))
```

##Lexical diversity
Predicting lexical diversity based on experimental condition, PAQ, demographics. 
```{r}
maximal_mod <- lmer(MTLD ~ condition  + age + gender + parent_ed +
                           (1| video), 
                         data = lmer_data)
summary(maximal_mod)

@@

M1 <- lex_means$mean[1]
M2 <- lex_means$mean[2]
SD1 <- lex_means$sd[1]
SD2 <- lex_means$sd[2]
